---
title: "Test RevealJS Loading Many Latex Files with Many Newcommands"
author: Fan Wang (fanwangecon.github.io)
date: May 4, 2020
output:
  revealjs::revealjs_presentation:
    theme: sky
    highlight: pygments
    center: false
    transition: none
    css: fan_present.css
    mathjax: local
    self_contained: false
    includes:
      in_header:
params:
    imgwidth: 25px
---

# Loading Many Latex Files with Many Newcommands

Need to avoid retyping latex newcommands which have many formated equations with parameters, symbols, and words that are concontrolled centrally.

# Loading Files from Another Directory

Usually the latex preamble files are stored somewhere else to work with the main paper draft tex file. 

## Load Tex from the same folder

```{r echo=TRUE, eval=FALSE}
test_tex_define_out = knitr::knit_child('tex_preamble.tex')
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```

```{r include=FALSE, eval=TRUE}
test_tex_define_out = knitr::knit_child('tex_preamble.tex')
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```
`r paste(test_tex_define_out, collapse='\n')`

<span style="font-size:40%;"> $$\exa$$ </span>
<span style="font-size:40%;"> $$\exb$$ </span>
<span style="font-size:40%;"> $$\exc$$ </span>

## Load Tex from the parallel folder

```{r echo=TRUE, eval=FALSE}
test_tex_define_out = knitr::knit_child('../fragments/tex_preamble.tex')
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```

```{r include=FALSE, eval=TRUE}
test_tex_define_out = knitr::knit_child('../fragments/tex_preamble.tex')
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```
`r paste(test_tex_define_out, collapse='\n')`

<span style="font-size:40%;"> $$\exd$$ </span>
<span style="font-size:40%;"> $$\exe$$ </span>
<span style="font-size:40%;"> $$\exf$$ </span>

## Load Tex from the parallel folder subfolder

```{r echo=TRUE, eval=FALSE}
test_tex_define_out = knitr::knit_child('../fragments/shorthand/tex_preamble.tex')
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```

```{r include=FALSE, eval=TRUE}
test_tex_define_out = knitr::knit_child('../fragments/shorthand/tex_preamble.tex')
test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
```
`r paste(test_tex_define_out, collapse='\n')`

<span style="font-size:40%;"> $$\exg$$ </span>
<span style="font-size:40%;"> $$\exh$$ </span>
<span style="font-size:40%;"> $$\exi$$ </span>

# Loading Multiple Latex Files Together with single input

Find all files with certain suffix in a folder, and then load them all in as child:

```{r echo=TRUE, eval=FALSE}
spt_root <- 'C:/Users/fan/Documents/Dropbox (UH-ECON)/repos/Tex4Econ/'
spt_texfolder <- 'nontex/revealjsrmd/math_tests/fragments/shorthand'
ls_path_group_use <- paste0(spt_root, spt_texfolder)
ls_sfls <- list.files(path=ls_path_group_use, recursive=T, pattern="short.*.tex", full.names=T)

test_tex_define_all <- ''
for (spt_file in ls_sfls) {
  test_tex_define_out = knitr::knit_child(spt_file)
  test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
  test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
  test_tex_define_all <- paste0(test_tex_define_all, test_tex_define_out)
}
```

```{r include=FALSE, eval=TRUE}
spt_root <- 'C:/Users/fan/Documents/Dropbox (UH-ECON)/repos/Tex4Econ/'
spt_texfolder <- 'nontex/revealjsrmd/math_tests/fragments/shorthand'
ls_path_group_use <- paste0(spt_root, spt_texfolder)
ls_sfls <- list.files(path=ls_path_group_use, recursive=T, pattern="short.*.tex", full.names=T)

test_tex_define_all <- ''
for (spt_file in ls_sfls) {
  test_tex_define_out = knitr::knit_child(spt_file)
  test_tex_define_out = gsub("\\%.*?\\\n", "", test_tex_define_out)
  test_tex_define_out = gsub("\\\n%.*","", test_tex_define_out)
  test_tex_define_all <- paste0(test_tex_define_all, test_tex_define_out)
}
```
`r paste(test_tex_define_all, collapse='\n')`

## Equations from Tex Preamble

These are equations created for paper:

$$\optirelainterceptyfullprc{\Ic}{\Icp}$$
$$\optirelaslopeyfullreorg{\Ic}{\Icp}$$

## More Equations from Tex Preamble

These are equations created for paper:

$$\optirelainterceptyfullreorg{\Ic}{\Icp}$$

## Longer Equation 

<span style="font-size:40%;">
\begin{align}
    \label{eq:disconstrainset}
    \begin{split}
    \Fconsds \equiv \Bigg\{
        \bm{\VD} =
        \left( \VD_1, \cdots, \VD_{\Nc} \right) :
        \VD_{\Ic} \in \Big\{ 0, 1, \dots, \VDhg \Big\}
        \text{, and, }
        \sum_{\Ic=1}^{\Nc} \VDc \le \VDagg \in \mathcal{N}_{+}
    \Bigg\}.\\
    \end{split}
\end{align}
</span>

There exist $\FDopti_{1}, \cdots, \FDopti_{\Nc}$ allocation mappings
\begin{align}
    \begin{split}
    \FDopti_{\Ic}\left(
      \VDagg, \Peq, \left\{\Pwgcp\right\}_{\Icp=1}^{\Nc}
                , \left\{\VAcp\right\}_{\Icp=1}^{\Nc},
                \left\{
                    \left\{\VM_{\Icp\Ik}\right\}_{\Ik = \VDlw}^{\VDhg}
                    \right\}_{\Icp=1}^{\Nc}
        \right)
    \end{split}
\end{align}

## Equations with Options 1

\eqtwoctsinvoptilub{\inon}{\intw}

## Equations with Options 2

\eqtwoctsoptilub{\inon}{\intw}

## Additional symbol testing

Using mathbf (does not work with greeks):

$mathbf\mathbf{this is bold} not bold$
$a + b \mathbf{+ a + b} + a + b$
$A + B \mathbf{+ A + B} + A + B$
$\alpha + \beta \mathbf{+ \alpha + \beta} + \alpha + \beta$

Using boldsymbol:

$boldsymbol\boldsymbol{this is boldsymbol} not boldsymbol$
$a + b \boldsymbol{+ a + b} + a + b$
$A + B \boldsymbol{+ A + B} + A + B$
$\alpha + \beta \boldsymbol{+ \alpha + \beta} + \alpha + \beta$